Prediction of 2024 US election ...

### 2024-11-02 paper/paper.qmd
update measurement

In this dataset, each row represents a polling question that records the variables of interest. Each entry allows us to explore the real-world relationships between polling factors and the support percentage (`pct`) for the candidates Kamala Harris and Donald Trump. This dataset enables an analysis of how various polling characteristics influence the reported support levels for the candidates we are focused.

>>>>

FiveThirtyEight’s polling measurement approach transforms raw polling data from multiple sources into one dataset by following a structured, multi-step process. First, it collects polling data from a variety of sources that meet its methodological and ethical standards. According to @radcliffe_538s_2023, polls included must disclose key details, such as the pollster’s name, survey dates, and the sampled population. FiveThirtyEight also excludes any hypothetical matchups or polls asking for general support of a party. The average result is reflected in the 'pct' column.

Next, FiveThirtyEight applies a series of adjustments to the data to account for sample size, timing, and pollster quality. As stated by @silver_polls_2008, the polls are weighted more heavily if they associate with larger sample. The sample size is documented in the data set as 'sample_size'. Poll recency is another critical factor, with newer polls weighted more to reflect current opinion trends. The 'pollscore' in the dataset is an indicator of pollster transparency and reliability in their methodology, according to @morris_trump_2024.

Further adjustments address polling biases, such as “house effects” (systematic leanings toward a particular candidate) and the mode of polling. Polls from partisan sources are included, but FiveThirtyEight applies a correction to counteract inherent biases [@morris_trump_2024].
